msc dissertation

### 2021-08-02 msc dissertation code.Rmd
latest

@@

lm1 <- lm(Discern ~ Real + Real*condition, data = pennystudy2r1)
summary(lm1)

@@

lm1 = lm(scale(pennystudy2r1$Discern) ~ condition, data = pennystudy2r1)
summary(lm1)

@@

```{r, message=FALSE}
pennystudy2r1$screen3_2

@@

pennystudy2plot1 <- pennystudy2r1 %>%
  select (c(1, 2, 3))

library(reshape2)

pennystudy2plot1 <- melt(pennystudy2plot1, id = 'condition')
head(pennystudy2plot1)

#Find out the sum for each type of news in different condition
p1 <- aggregate(value~condition+variable, data = pennystudy2plot1, FUN = sum)

ggplot(p1, aes(x = condition, y = value / 428, fill = variable)) + 
  geom_bar(stat = 'identity',position = 'dodge')

>>>>

#replace NA to 0 in screen 1,2,3

pennystudy2r1[c("screen1","screen2","screen3")][is.na(pennystudy2r1[c("screen1","screen2","screen3")])] <- 0

#create dummy column, add screen 1,2,3 together. Screen = 3 indicate success in all attention check
pennystudy2r1['dummycheck']=pennystudy2r1['screen1'] + pennystudy2r1['screen2'] + pennystudy2r1['screen3']

#like the researcher did, change data frame from wide to long
##first drop unnecessary column
pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,10,14))

##Add ID column
pennys2r1long <- tibble::rowid_to_column(pennys2r1long, "ID")

## change from wide to long
library(tidyr)

keycol <- "newstype"
valuecol <- "measurement"
gathercols <- c("Fake","Real")

pennys2r1long <- gather_(pennys2r1long, keycol, valuecol, gathercols)

##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one

merge(pennystudy2r1, pennys2r1long, by.x='condition', by.y='ID')

##organize data by ID, then reorder the column
pennys2r1long <- pennys2r1long[order(pennys2r1long$ID),]

pennys2r1long <- pennys2r1long[, c(1, 2, 6, 7, 4, 5, 3)]

##separating the data based on number of successful attention check

### attention check above and equal to 1
pennys2r1longa1 <- subset(pennys2r1long, dummycheck %in% c("1","2","3"))

### attention check above and equal to 2
pennys2r1longa2 <- subset(pennys2r1long, dummycheck %in% c("2","3"))

### attention check equal to 3
pennys2r1longa3 <- subset(pennys2r1long, dummycheck %in% c("3"))

@@

lm1 <- lm(veracity ~ newstype + newstype*condition, data = pennys2r1longa2)
summary(lm1)

@@

install.packages("effectsize")
library(effectsize)

cohens_d(pennystudy2r1)

@@

### graph 1: including all
```{r, message=FALSE}

@@

#Since the plot not specify which condition they use, then I need to plot all 4 graph in different condition

#condition 1: all

pennystudy2plot1 <- pennys2r1long %>%
  select (c(1, 2, 3, 4))

#Find out the sum for each type of news in different condition
p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, FUN = sum)

##double check for correctness
sum(pennystudy2plot1$measurement,na.rm = TRUE)

#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
ggplot(p1, aes(x = condition, y = measurement/428, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```
### graph 2 attention check above and equal to 1

#condition 2: above and equal to 1

pennystudy2plot2 <- pennys2r1longa1 %>%
  select (c(1, 2, 3, 4))

#Find out the sum for each type of news in different condition
p2 <- aggregate(measurement~condition+newstype, data = pennystudy2plot2, FUN = sum)

##double check for correctness
sum(pennystudy2plot2$measurement,na.rm = TRUE)

#since the obs is 1664, thus 1664/2 = 832 participants. So to get percentage of sharing intention each fake and real news need to divided by 832/2 = 416
ggplot(p2, aes(x = condition, y = measurement/416, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/416, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```

### graph 3 attention check above and equal to 2
```{r, message=FALSE}
#condition 3: above and equal to 2
pennystudy2plot3 <- pennys2r1longa2 %>%
  select (c(1, 2, 3, 4))

#Find out the sum for each type of news in different condition
p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, FUN = sum)

##double check for correctness
sum(pennystudy2plot3$measurement,na.rm = TRUE)

#since the obs is 1292 for attention > 2, thus 1292/2 = 646 participants. So to get percentage of sharing intention each fake and real news need to divided by 646/2 = 323
ggplot(p3, aes(x = condition, y = measurement/323, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/323, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```

### graph 4 attention check equal to 3
```{r, message=FALSE}
#condition 3: equal to 3
pennystudy2plot4 <- pennys2r1longa3 %>%
  select (c(1, 2, 3, 4))

#Find out the sum for each type of news in different condition
p4 <- aggregate(measurement~condition+newstype, data = pennystudy2plot4, FUN = sum)

##double check
sum(pennystudy2plot4$measurement,na.rm = TRUE)

#since the obs is 460 for attention = 3, thus 460/2 = 230 participants. So to get percentage of sharing intention each fake and real news need to divided by 230/2 = 115
ggplot(p4, aes(x = condition, y = measurement/115, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/115, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```
